{\it Proposal:}\\ Ultrashort pulsed microwave viral envelope disruption as a COVID-19 treatment

### 2020-10-24 documents/charge.tex
Run 5 prep

Yang et al determine that, to fit their microwave absorption cross-section data, the "core" and "shell" of the virus should have an effective charge of about $10^7 e^-$.

@@

@@

of course, much of the potential energy may have already existed in the host cell, so this is probably an invalid comparison. And if most of the charge is contributed by osmotic, ion , this potential energy may not be counted.

>>>>

Back-of-the-envelope.

Yang et al determine that, to fit their microwave absorption cross-section data and produce the decrease in infectivity via the route they suggest, the "core" and "shell" of the virus should have an effective charge of about $10^7 e^-$.

@@

\section{Hello World}
\subsection{Hello World}
\label{sec:hello}

\hyperref[sec:hello]{See section.}

Rather than, for instance, less than 1/100 for Arginine or 1/600 for DNA.

@@

of course, much of the potential energy may have already existed in the host cell, so this is probably an invalid comparison. And if most of the charge is contributed by osmotic, ion , this potential energy may not be considered in the above.
